02_limma_hyp_grouped

### 2019-04-03 analysis/02_limma_hyp_grouped.Rmd
new groupings

---
title: "04_limma_gon_F"
output: md_document
---

This anlaysis will _exclude_ the control timepoint and will example males and females separately.

@@

knitr::opts_chunk$set(fig.path = '../figures/gon_F/',cache=TRUE)
```

# Females first

@@

```{r filter}
colData <- colData %>%
  dplyr::filter(grepl('gonad', tissue)) %>%
  dplyr::filter(treatment != "control") %>%
  dplyr::filter(sex == "female") %>%
  droplevels()
row.names(colData) <- colData$V1

# print sample sizes
colData %>% select(treatment, tissue)  %>%  summary()

@@

Then, I followed the steps from <https://github.com/macmanes-lab/RockDove/blob/master/parental_care/parental_analysis.Rmd>.

@@

```{r plotMDS}
levels(colData$treatment)
col.treatment <- c("#a6cee3", "#1f78b4", "#b2df8a", "#33a02c", "#fb9a99", "#e31a1c", "#fdbf6f", "#ff7f00", "#cab2d6")[colData$treatment]
myfill <- c("#a6cee3", "#1f78b4", "#b2df8a", "#33a02c", "#fb9a99", "#e31a1c", "#fdbf6f", "#ff7f00", "#cab2d6")

plotMDS(parentalobject, cex = 0.5, labels = colData$treatment, col=col.treatment)
title("Female Gonad MDS 1v2")
plotMDS(parentalobject, cex = 0.5, labels = colData$treatment, col=col.treatment, dim=c(3,4))
title("Female Gonad MDS 3v4")
plotMDS(parentalobject, cex = 0.5, labels = colData$treatment, col=col.treatment, dim=c(5,6))
title("Female Gonad MDS 5v6")
```

@@

# subset of conrasts - sex specific comparing hatch to lay
my.contrasts <- makeContrasts(
	         FG_BL = female.gonad.bldg - female.gonad.lay,
	         FG_Li3 = female.gonad.lay - female.gonad.inc.d3,
	         FG_i3i9 = female.gonad.inc.d3 - female.gonad.inc.d9,
	         FG_i9i17 = female.gonad.inc.d9 - female.gonad.inc.d17,
	         FG_i17H = female.gonad.inc.d17 - female.gonad.hatch,
	         FG_Hn5 = female.gonad.hatch -  female.gonad.n5,
	         FG_n5n9 = female.gonad.n5 - female.gonad.n9,

	         FG_Bi3 = female.gonad.bldg - female.gonad.inc.d3,
	         FG_Bi9 = female.gonad.bldg - female.gonad.inc.d9,
	         FG_Bi17 = female.gonad.bldg - female.gonad.inc.d17,
	         FG_BH = female.gonad.bldg - female.gonad.hatch,
	         FG_Bn5 = female.gonad.bldg - female.gonad.n5,
	         FG_Bn9 = female.gonad.bldg - female.gonad.n9,

	         FG_Li9 = female.gonad.lay - female.gonad.inc.d9,
           FG_Li17 = female.gonad.lay - female.gonad.inc.d17, 
	         FG_LH = female.gonad.lay - female.gonad.hatch,
	         FG_Ln5 = female.gonad.lay - female.gonad.n5,
	         FG_Ln9 = female.gonad.lay - female.gonad.n9,

	         FG_i3i17 = female.gonad.inc.d3 - female.gonad.inc.d17,
	         FG_i3H = female.gonad.inc.d3 - female.gonad.hatch,
	         FG_i3n5 = female.gonad.inc.d3 - female.gonad.n5,
	         FG_i3n9 = female.gonad.inc.d3 - female.gonad.n9,

	         FG_i9H = female.gonad.inc.d9 - female.gonad.hatch,
	         FG_i9n5 = female.gonad.inc.d9 - female.gonad.n5,
	         FG_i9n9 = female.gonad.inc.d9 - female.gonad.n9,

	         FG_i17n5 = female.gonad.inc.d17 - female.gonad.n5,
	         FG_i17n9 = female.gonad.inc.d17 - female.gonad.n9,

	         FG_Hn9 = female.gonad.hatch -  female.gonad.n9,

levels=parentaldesign)

colnames(my.contrasts)

# create a list with all the two way contrasts

mycontrasts <- colnames(my.contrasts)
mycontrasts

>>>>

---
title: "02_limma_hyp_grouped"
output: md_document
---

@@

knitr::opts_chunk$set(fig.path = '../figures/hyp_grouped/',cache=TRUE)
```

This anlaysis will _exclude_ the control timepoint but _combine_ incubation and nestling timepoints.

@@

```{r}
# making new groups
colData$group <- NULL
colData$tempgroup <- ifelse(colData$treatment == "bldg", "bldg",
                  ifelse(colData$treatment == "control", "control",
                   ifelse(colData$treatment == "hatch", "hatch",
                    ifelse(grepl("inc", colData$treatment), "inc",
                     ifelse(colData$treatment == "lay", "lay", "nestl")))))
colData$tempgroup <- as.factor(colData$tempgroup)

colData$group <- paste(colData$sex, colData$tempgroup, sep = "")
colData$group <- as.factor(colData$group)
str(colData$group)
```

```{r filter}
colData <- colData %>%
  dplyr::filter(grepl('hypothalamus', tissue)) %>%
  dplyr::filter(treatment != "control") %>%
  #dplyr::filter(sex == "female") %>%
  droplevels()
row.names(colData) <- colData$V1

# print sample sizes
colData %>% select(group, tissue)  %>%  summary()

@@

@@

```{r plotMDS}
levels(colData$group)
col.group <- c("#a6cee3", "#1f78b4", "#b2df8a", "#33a02c", "#fb9a99",
               "#a6cee3", "#1f78b4", "#b2df8a", "#33a02c", "#fb9a99")[colData$group]
myfill <- c("#a6cee3", "#1f78b4", "#b2df8a", "#33a02c", "#fb9a99",
            "#a6cee3", "#1f78b4", "#b2df8a", "#33a02c", "#fb9a99")

plotMDS(parentalobject, cex = 0.5, labels = colData$group, col=col.group)
title("MDS 1v2")
plotMDS(parentalobject, cex = 0.5, labels = colData$group, col=col.group, dim=c(3,4))
title("MDS 3v4")
plotMDS(parentalobject, cex = 0.5, labels = colData$group, col=col.group, dim=c(5,6))
title("MDS 5v6")
```

@@

# subset of conrasts - sex specific comparing hatch to lay
my.contrasts <- makeContrasts(
	         femaleBL = femalebldg - femalelay,
	         femaleLI = femalelay - femaleinc,
	         femaleIH = femaleinc - femalehatch,
	         femaleHN = femalehatch -  femalenestl,
	         femaleBL = femalebldg - femaleinc,
	         femaleBL = femalebldg - femalehatch,
	         femaleBL = femalebldg - femalenestl,
	         femaleLH = femalelay - femalehatch,
	         femaleLN = femalelay - femalenestl,
	         femaleHN = femalehatch - femalenestl,

	         maleBL = malebldg - malelay,
	         maleLI = malelay - maleinc,
	         maleIH = maleinc - malehatch,
	         maleHN = malehatch -  malenestl,
	         maleBL = malebldg - maleinc,
	         maleBL = malebldg - malehatch,
	         maleBL = malebldg - malenestl,
	         maleLH = malelay - malehatch,
	         maleLN = malelay - malenestl,
	         maleHN = malehatch - malenestl,

	         fm_B = femalebldg - malebldg,
	         fm_L = femalelay - malelay,
	         fm_I = femaleinc - maleinc,
	         fm_H = femalehatch - malehatch,
	         fm_N = femalenestl - malenestl,
levels=parentaldesign)

# create a list with all the two way contrasts
mycontrasts <- colnames(my.contrasts)
